\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}


\usepackage[
  a4paper,
  left=3cm,
  right=2cm,
  top=3cm,
  bottom=5cm,
]{geometry}




\input{glyphtounicode}

% Font options (default Computer Modern)
% Font options
\usepackage[scaled]{helvet}
\renewcommand\familydefault{\sfdefault}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.65in}
\addtolength{\evensidemargin}{-0.65in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.3in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}



% Section formatting
\titleformat{\section}{}{}{0em}{}[\titlerule]

% Ensure PDF is machine readable
\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{\item\small{#1}}
\newcommand{\resumeSubheading}[4]{
  \vspace{2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\stack}[1]{\item\small{\textbf{Stack: } #1}\vspace{-5pt}} 
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingList}{\begin{itemize}[leftmargin=0.16in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.2in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\SectionTitle}{\Large\bfseries\scshape\raggedright}


\begin{document}

\begin{center}
  \textbf{\Huge Rifky Adni Putra} \\
  \small +62 831 049 04353 $|$ \href{mailto:rifkyadp@gmail.com}{rifkyadp@gmail.com} $|$ 
  \href{https://linkedin.com/in/rifptra}{linkedin.com/in/rifptra} $|$
  \href{https://github.com/rifkyputra}{github.com/rifkyputra} \\
\end{center}

\section{\SectionTitle {Summary}}
Fullstack Software Engineer with over 5 years of experience architecting resilient, scalable systems across the Singaporean and Southeast Asian tech landscapes. Experienced in Node.js and Go, with a deep background in Cloud-Native infrastructure (KCNA \& KCSA) and AWS to support high-volume data queries and scalable architectures. Proven track record in full-stack and mobile development, enabling the design of high-efficiency, client-optimized APIs and user-friendly UIs. Passionate about leveraging AI-powered solutions to transform higher education and student career readiness. Experienced in fast-paced, remote, and VUCA environments, with a strong desire to help build a global-standard AI B2B SaaS enterprise from Southeast Asia.

\section{\SectionTitle {Work Experience}}
\resumeSubHeadingList
  \resumeSubheading
      {Software Engineer}{Jan 2025 -- Jan 2026}
      {EngageRocket Pte. Ltd. (Employee Engagement Platform)}{Singapore, SG - Remote}
      \resumeItem{\textbf{Stack:} Go, Node.js, PostgreSQL, Redis, Docker, Kubernetes, AWS}
      \resumeSubHeadingList
          \resumeItem{\textbullet\ Engineered a resilient data ingestion pipeline to process 100k+ row Excel uploads; implemented stateful, recoverable logic to ensure data integrity.}
          \resumeItem{\textbullet\ Developed a graph-based organizational structure feature using React and Go, optimizing complex hierarchical data visualization for enterprise clients.}
          \resumeItem{\textbullet\ Handled production incident resolution during on-call rotations, maintaining high system availability.}
          \resumeItem{\textbullet\ Established front-end testing standards (Jest/React Testing Library), increasing coverage from 0\% to 30\% and reducing regression bugs in the core product.}
          \resumeItem{\textbullet\ Developed core modules with clean, scalable architecture that supports future AI integrations.}
      \resumeSubHeadingListEnd
  \resumeSubheading
      {Senior Full Stack Developer}{July 2023 -- Jan 2025}
      {ABBA Maintenance Pte. Ltd. (Home cleaning company)}{Singapore, SG - Remote} \\
      \resumeItem{\textbf{Stack:} Hono (Node.js), React.js/Next.js, PostgreSQL, tRPC, RabbitMQ, AWS}
      \resumeSubHeadingList
          \resumeItem{\textbullet\ Developed and deployed an employee management platform.}
          \resumeItem{\textbullet\ Tracked real-time employee locations and displayed the nearest worker to each client improving dispatch efficiency and reducing manual coordination time.}
          \resumeItem{\textbullet\ Created Github Action CI/CD pipeline to ensure fast iteration.}
          \resumeItem{\textbullet\ Architected backend APIs and optimized data flows across distributed systems.}
          \resumeItem{\textbullet\ Directed and supervise interns from National University of Singapore.}
      \resumeSubHeadingListEnd
  \resumeSubheading
      {Software Engineer}{May 2020 -- July 2023}
      {PT Berau Coal Energy Tbk (Mining, Sinarmas Group - Indonesian Conglomerates)}{Jakarta, ID}
      \resumeItem{\textbf{Stack:} Node.js (Koa.js), Vue, Flutter, Express(Node.js), MongoDB, AWS}
      \resumeSubHeadingList
          \resumeItem{\textbullet\ Built mobile apps for mining operation with remote location constraint. full offline mode sync capability.}
          \resumeItem{\textbullet\ Code Contributor to internal web applications supporting mining operations.}
          \resumeItem{\textbullet\ Develop Solar Panel Installation App.}
          \resumeItem{\textbullet\ Contributed to the company's transition toward paperless workflows.}
      \resumeSubHeadingListEnd
\resumeSubHeadingListEnd


\section{\SectionTitle{Projects}}
\resumeSubHeadingList


\resumeSubheading
      {TraceHub}{January 2025 -- Present}
      {Author}{Nest.js(Node.js), React.js, RabbitMQ, PostgreSQL}
      \resumeItem{NestJS-based traceability and audit platform that manages product formulas, procurement, QC workflows, production batches with FIFO material consumption, inventory, and exportable compliance reports. Implemented domain models, PostgreSQL-backed REST APIs, and end-to-end traceability enabling immutable audit trails and streamlined regulatory investigations}

      
\resumeSubheading
      {Medical AI Assistant}{January 2025}
      {Author}{FastAPI, LangGraph, MCP, React.js}
      \resumeItem{Built a medical triage assistant with FastAPI + LangGraph routing, MCP tools for interoperability, and a streaming React chat UI; delivers cholesterol/diabetes risk assessments, first-aid guidance, and WebSocket live responses backed by OpenRouter LLM.}

  
  \resumeSubheading
      {Galeriee (galeri.ee)}{Oct 2025 -- Nov 2025}
      {Author}{Tanstack Start, Convex, ffmpeg, R2, Turso}
      \resumeItem{ Full-stack collaborative gallery app with role-based authentication, ffmpeg compression, email invitations, and a serverless architecture.}
      
  \resumeSubheading
      {Jakarta Eye Center Apps}{Dec 2021 -- Dec 2023} 
      {Freelance Mobile App Developer}{Flutter}
      \resumeItem{Led Discovery Phases for new feature sets, transforming client feedback into a prioritized Product Backlog and clear Acceptance Criteria for the development team, implementing robust API integrations and asynchronous payment processing. resulting an increase of user retention and customer satisfaction}

  \resumeSubheading
      {iSAFE BIB}{April 2020 -- Aug 2023} 
      {Software Engineer}{Flutter}
      \resumeItem{Developed a comprehensive health, safety, and environment app with offline mode support, catering to 500+ daily active users in remote areas, ensuring continuity of service and high reliability, Spearheaded Major upgrade and rewrite from React Native to Flutter. Major Upgrade from Flutter 1 to Flutter 2 increasing type checking resulting in lesser bugs. Huge codebase up to 100k lines of codes.}
\resumeSubheading
      {SunTerra}{April 2020 -- Sept 2023} 
      {Software Engineer}{Flutter}
      \resumeItem{Solar Panel Installation app supporting Client and Vendor Apps}

  \resumeSubheading
      {Open Source Projects}{Jan 2020 -- Present} 
      {Authors \& Contributors}{Bash, Dart, Flutter, Rust, React.js, etc.}
      \resumeSubHeadingList
          \resumeItem{\textbullet\ \textbf{Networking tools:} sshii} 
          \resumeItem{\textbullet\ \textbf{Linux Desktop:} KppleMenu}
          \resumeItem{\textbullet\ \textbf{Experimentals:} honotan, dart’s shelf article API, firebase face recognition, rust actix api, todoids, soundboard pwa}
      \resumeSubHeadingListEnd
\resumeSubHeadingListEnd

\section{\SectionTitle{Technical Skills}}
\resumeSubHeadingList
  \resumeItem{\textbf{Core Backend}: Node.js (NestJS, Hono, Express), Go (Chi, Fiber, Echo), FastAPI TypeScript, Python}
  \resumeItem{\textbf{Cloud \& Infrastructure}: Kubernetes (KCNA/KCSA Certified), AWS (EC2, S3, ECS, RDS), Docker, CI/CD (GitHub Actions), Cloudflare(R2, Workers, D1 Database), Google Cloud}
  \resumeItem{\textbf{Database \& Data}: PostgreSQL, Redis, MongoDB, RabbitMQ (Messaging), PostGIS}
  \resumeItem{\textbf{Testing \& Quality}: Jest, Vitest, React Testing Library}
  \resumeItem{\textbf{Cross-Functional}: React.js, Next.js, Tanstack Start, Svelte, Flutter (Mobile), System Design}
  \resumeItem{\textbf{GIS}: PostGIS, Google Maps API }
  \resumeItem{\textbf{Dev Platforms}: Firebase, Supabase, Convex }
  \resumeItem{\textbf{Scripting}: Bash, Python, Bun }
  \resumeItem{\textbf{AI/Automation}: LangChain, LangGraph, RAG }
  \resumeItem{\textbf{Architecture}: Microservices, Event-Driven Architecture, Monolithic, CQRF, RESTful APIs, tRPC, WebSockets, Serverless}
\resumeSubHeadingListEnd



\section{\SectionTitle{Certifications}}
\resumeSubHeadingList
\resumeSubheading
{KCNA: Kubernetes and Cloud Native Associate}{Issued Dec 2025 · Expires Dec 2027}
{The Linux Foundation}{}
\resumeItem{Credential ID LF-qc5h22ipix}

\resumeSubheading
{KCSA: Kubernetes and Cloud Native Security Associate}{Issued Dec 2025 · Expires Dec 2027}
{The Linux Foundation}{}
\resumeItem{Credential ID LF-r4zzn7mh1x}

\resumeSubheading
{Amazon Aurora PostgreSQL and Amazon RDS PostgreSQL}{Issued May 2024}
{Amazon Web Services (AWS)}{}

\resumeSubheading
{Introduction to Amazon Elastic Container Service}{Issued Nov 2022}
{Amazon Web Services (AWS)}{}

\resumeSubheading
{Microsoft Certified: Azure Fundamentals}{Issued Nov 2022}
{Microsoft}{}

\resumeSubheading
{IT Bootcamp for Vocational School at SMM (Batch 1)}{Issued May 2022}
{PT Enigma Cipta Humanika}{}


\resumeSubHeadingListEnd

\section{\SectionTitle {Education}}
\resumeSubHeadingList
  \resumeSubheading
      {INDRAPRASTA PGRI UNIVERSITY}{ }
      {Major in Informatics Engineering}{ - } 
      \resumeSubHeadingList
      \resumeItem{\textbullet\ Learning: Computer Science, Operating Systems; Algorithms; Data Structure; OOP}
      \resumeSubHeadingListEnd
  \resumeSubheading
      {Enigma Camp}{ } 
      {IT Bootcamp Graduate}{2020} 
      \resumeSubHeadingList
      \resumeItem{\textbullet\ Learning: Flutter; React.js; Agile;}
      \resumeSubHeadingListEnd
\resumeSubHeadingListEnd

\section{\SectionTitle{Additionals}}
\resumeSubHeadingList
      \resumeItem{\textbf{Languages:} English, Indonesian}{} \\
\resumeSubHeadingListEnd

\end{document}