\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\usepackage[
  a4paper,
  left=3cm,
  right=2cm,
  top=3cm,
  bottom=5cm,
]{geometry}




\input{glyphtounicode}

% Font options (default Computer Modern)
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.3in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}



% Section formatting
\titleformat{\section}{}{}{0em}{}[\titlerule]

% Ensure PDF is machine readable
\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{\item\small{#1}}
\newcommand{\resumeSubheading}[4]{
  \vspace{2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\stack}[1]{\item\small{\textbf{Stack: } #1}\vspace{-5pt}} 
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingList}{\begin{itemize}[leftmargin=0.16in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.2in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\SectionTitle}{\Large\bfseries\scshape\raggedright}

\begin{document}

\begin{center}
  \textbf{\Huge Rifky Adni Putra} \\
  \small This resume is generated from LaTeX source code. please visit www.pir.my.id and use contact form to reach out. $|$ 
  \href{https://linkedin.com/in/rifptra}{linkedin.com/in/rifptra} $|$
  \href{https://github.com/rifkyputra}{github.com/rifkyputra} \\
  \href{https://pir.my.id}{www.pir.my.id}
\end{center}

\section{\SectionTitle {Summary}}
Software Engineer specializing in modern web technologies with strong experience in building scalable, reliable, and accessible applications across HR Tech, Industrial Mining, and Healthcare sectors. Expert in React.js and Node.js with a background spanning frontend, backend, and mobile development. Proven ability to ship high-quality features, modernize legacy systems, and optimize performance across distributed environments. Strong ownership, fast learning, and comfortable working in ambiguous problem spaces. Passionate about solving real-world problems with modern and pragmatic full-stack approaches.

\section{\SectionTitle {Work Experience}}
\resumeSubHeadingList
  \resumeSubheading
      {Software Engineer}{Jan 2025 -- Jan 2026}
      {EngageRocket Pte. Ltd. (Employee engagement platform)}{Singapore, SG - Remote}
      \resumeItem{\textbf{Stack:} React.js, Go, PostgreSQL, Redis, Docker, Kubernetes, AWS }
      \resumeSubHeadingList
          \resumeItem{\textbullet\ Develop new features and fix bugs in legacy code.}
          \resumeItem{\textbullet\ Implemented graph based layout in new org structure feature.}
          \resumeItem{\textbullet\ Participated in on-call rotations to diagnose and resolve production incidents, improving SLA and system uptime.} 
          \resumeItem{\textbullet\ Established front-end testing standards using Jest, React Testing Library, improving test coverage from 0\% to 30\%, reducing regression test workload.}
      \resumeSubHeadingListEnd
  \resumeSubheading
      {Senior Full Stack Developer}{May 2024 -- Jan 2025}
      {ABBA Maintenance Pte. Ltd. (Home cleaning company)}{Singapore, SG - Remote} \\
      \resumeItem{\textbf{Stack:} Hono, React.js/Next.js, PostgreSQL, tRPC, RabbitMQ, AWS}
      \resumeSubHeadingList
          \resumeItem{\textbullet\ Developed and deployed an employee management platform.}
          \resumeItem{\textbullet\ Tracked real-time employee locations and displayed the nearest worker to each client.}
          \resumeItem{\textbullet\ Created Github Action CI/CD pipeline.}
          \resumeItem{\textbullet\ Architected backend APIs and optimized data flows across distributed systems.}
          \resumeItem{\textbullet\ Directed and supervise interns from National University of Singapore.}
      \resumeSubHeadingListEnd
  \resumeSubheading
      {Flutter Developer}{Aug 2023 -- May 2024}
      {PT Ewide Indonesia (Software Agency, EwidePlus Korea branch)}{Jakarta, ID}
      \resumeItem{\textbf{Stack:} Flutter, React.js}
      \resumeSubHeadingList
          \resumeItem{\textbullet\ Built mobile apps for Education Sector.}
          \resumeItem{\textbullet\ Collaborated with cross-functional teams to deliver solutions.}
          \resumeItem{\textbullet\ Oversee and give consultation to vendor for the best practices.}
          \resumeItem{\textbullet\ Built and deployed a Carbon Calculator product from scratch.}
          \resumeItem{\textbullet\ Managed the full mobile application release cycle to both the Apple App Store and Google Play Store.}
      \resumeSubHeadingListEnd
  \resumeSubheading
      {Software Engineer}{May 2020 -- Aug 2023}
      {PT Berau Coal Energy Tbk (Mining, Sinarmas Group - Indonesian Conglomerates)}{Jakarta, ID}
      \resumeItem{\textbf{Stack:} Node.js (Koa.js), Vue, Flutter, Express, MongoDB, AWS}
      \resumeSubHeadingList
          \resumeItem{\textbullet\ Built mobile apps for mining operation with remote location constraint. full offline mode sync capability.}
          \resumeItem{\textbullet\ Code Contributor to internal web applications supporting mining operations.}
          \resumeItem{\textbullet\ Develop Solar Panel Installation App.}
          \resumeItem{\textbullet\ Contributed to the company's transition toward paperless workflows.}
      \resumeSubHeadingListEnd
\resumeSubHeadingListEnd


\section{\SectionTitle{Projects}}
\resumeSubHeadingList

\resumeSubheading
      {Medical AI Assistant}{January 2025 -- Present}
      {Author}{FastAPI, LangGraph, MCP, React}
      \resumeItem{Built a medical triage assistant with FastAPI + LangGraph routing, MCP tools for interoperability, and a streaming React chat UI; delivers cholesterol/diabetes risk assessments, first-aid guidance, and WebSocket live responses backed by OpenRouter LLM.}

  
  \resumeSubheading
      {Galeriee (galeri.ee)}{Oct 2025 -- Nov 2025}
      {Author}{Tanstack Start, ffmpeg, R2, Turso}
      \resumeItem{ Full-stack collaborative gallery app with role-based authentication, ffmpeg compression, email invitations, and a serverless architecture.}
      
  \resumeSubheading
      {Jakarta Eye Center Apps}{Dec 2021 -- Dec 2023} 
      {Freelance Mobile App Developer}{Flutter}
      \resumeItem{Led Discovery Phases for new feature sets, transforming client feedback into a prioritized Product Backlog and clear Acceptance Criteria for the development team, implementing robust API integrations and asynchronous payment processing. resulting an increase of user retention and customer satisfaction}

  \resumeSubheading
      {iSAFE BIB}{April 2020 -- Aug 2023} 
      {Software Engineer}{Flutter}
      \resumeItem{Developed a comprehensive health, safety, and environment app with offline mode support, catering to 500+ daily active users in remote areas, ensuring continuity of service and high reliability, Spearheaded Major upgrade and rewrite from React Native to Flutter. Major Upgrade from Flutter 1 to Flutter 2 increasing type checking resulting in lesser bugs. Huge codebase up to 100k lines of codes.}
\resumeSubheading
      {SunTerra}{April 2020 -- Sept 2023} 
      {Software Engineer}{Flutter}
      \resumeItem{Solar Panel Installation app supporting Client and Vendor Apps}

  \resumeSubheading
      {Open Source Projects}{Jan 2020 -- Present} 
      {Authors \& Contributors}{Bash, Dart, Flutter, Rust, React.js, etc.}
      \resumeSubHeadingList
          \resumeItem{\textbullet\ \textbf{Networking tools:} sshii, uwuhomelab.} 
          \resumeItem{\textbullet\ \textbf{Linux Desktop:} KppleMenu}
          \resumeItem{\textbullet\ \textbf{Experimentals:} honotan, fiochat, dart’s shelf article API, firebase face recognition, rust actix api, todoids, soundboard pwa}
      \resumeSubHeadingListEnd
\resumeSubHeadingListEnd

\section{\SectionTitle{Technical Skills}}
\resumeSubHeadingList

  \resumeItem{\textbf{Programming Languages}: TypeScript (Advanced), Dart (Advanced), Go (intermediate), Python (intermediate), Bash (Basic).}
  
  \resumeItem{\textbf{Frontend/Mobile}: React.js, Flutter, TanStack Start, SvelteKit, GSAP, Rive, Lottie, Bloc, Riverpod, Redux, Zustand, MobX, Better Auth, React Flow, vite, zod }
  \resumeItem{\textbf{Backend}: NestJS, Hono, FastAPI, express.js Chi(Go), Fiber, BullMQ, RabbitMQ}
  \resumeItem{\textbf{Database}: Sqlite, PostgreSQL, Redis, MySQL, MongoDB }
  \resumeItem{\textbf{Testing}: Jest, Bun Test, Vitest, React Testing Library, lcov }
  \resumeItem{\textbf{Cloud}: Cloudflare worker,Cloudflare R2, AWS EC2, AWS S3, AWS ECS }
  \resumeItem{\textbf{Logging}: Sentry, Crashlytics, Axiom }
  \resumeItem{\textbf{GIS}: PostGIS, Google Maps API }
  \resumeItem{\textbf{CI/CD}: Github Action, Gitlab Runner }
  \resumeItem{\textbf{Containerization}: Docker, Kubernetes }
  \resumeItem{\textbf{Dev Platforms}: Firebase, Supabase, Convex }
  \resumeItem{\textbf{Scripting}: Bash, Python, Bun }
  \resumeItem{\textbf{AI/Automation}: n8n, LangChain, RAG }
  \resumeItem{\textbf{Architecture}: Microservices, Event-Driven Architecture, Monolithic, CQRF, RESTful APIs, tRPC, WebSockets, Serverless}
\resumeSubHeadingListEnd



\section{\SectionTitle{Certifications}}
\resumeSubHeadingList
\resumeSubheading
{KCNA: Kubernetes and Cloud Native Associate}{Issued Dec 2025 · Expires Dec 2027}
{The Linux Foundation}{}
\resumeItem{Credential ID LF-qc5h22ipix}

\resumeSubheading
{KCSA: Kubernetes and Cloud Native Security Associate}{Issued Dec 2025 · Expires Dec 2027}
{The Linux Foundation}{}
\resumeItem{Credential ID LF-r4zzn7mh1x}

\resumeSubheading
{Amazon Aurora PostgreSQL and Amazon RDS PostgreSQL}{Issued May 2024}
{Amazon Web Services (AWS)}{}

\resumeSubheading
{Introduction to Amazon Elastic Container Service}{Issued Nov 2022}
{Amazon Web Services (AWS)}{}

\resumeSubheading
{Microsoft Certified: Azure Fundamentals}{Issued Nov 2022}
{Microsoft}{}

\resumeSubheading
{IT Bootcamp for Vocational School at SMM (Batch 1)}{Issued May 2022}
{PT Enigma Cipta Humanika}{}


\resumeSubHeadingListEnd

\section{\SectionTitle {Education}}
\resumeSubHeadingList
  \resumeSubheading
      {INDRAPRASTA PGRI UNIVERSITY}{ }
      {Major in Informatics Engineering}{ - } 
      \resumeSubHeadingList
      \resumeItem{\textbullet\ Learning: Operating Systems; Algorithms; Data Structure; OOP}
      \resumeSubHeadingListEnd
  \resumeSubheading
      {Enigma Camp}{ } 
      {IT Bootcamp Graduate}{2020} 
      \resumeSubHeadingList
      \resumeItem{\textbullet\ Learning: Flutter; React.js; Agile;}
      \resumeSubHeadingListEnd
\resumeSubHeadingListEnd

\section{\SectionTitle{Additionals}}
\resumeSubHeadingList
      \resumeItem{\textbf{Languages:} English, Indonesian}{} \\
      \resumeItem{\textbf{Interest/Hobbies:} Water Sports, Snorkeling}{ } 
\resumeSubHeadingListEnd

\end{document}